%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Biology
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Earth, biosphere
%% Water, chemical elements
%% Inorganic vs Organic Material
%% Evolution
%% DNA, Mutations, Replication
%%
%% Simple organisms, more complex organisms
%% Animals
%% Human Beings
%%

\section{Biology Concepts}

Human beings may have 100 trillion cells. There are several hundred distinct
human cell types.

The most basic cells may have a cell wall, chromosomes, plasma membrane,
fibrils, ribosomes.

DNA is the blue print for life of a cell.  It mostly static, mutations may be
introduced.   DNA contains the instructions for a cell's structure and function.
It is the blueprint for how the cell runs, reproduces, builds and repairs
itself, and every other function necessary for cell life.  Metabolism is a
chemical reaction

A protein is a generic term for anything that is made of amino acids.  Proteins
are considered the "cellular machinery"; they are constantly being synthesized, and play many essential structural and enzymatic roles within the
cell.  How does a cell die?  Proteisn sythensis may be interrupted.  Protein
synthesis uses about 75 percent of a cell'ss energy. Protein is a macromolceule
Macromolecules that make up cell material

Bacterial cells can change patterns of enzymes, in order to adapt them to their
specific environment.

With traits,  in order to show-up, a dominant trait needs only one trait unit
from one of the parents, and the recessive one needs two, from both parents, in order to prevail, 
that is the reason why the ratio between occurrences of dominant traits and
recessive traits is. The same explanation applies to the shape traits.

keywords: earth, biosphere, inorganic vs organic material,
water, DNA, mutations, replication, simple organisms, more complex organisms,
animals, human beings, life, death, mutations, evolution, blind
watchmaker, mitochrondria, flagella, pili, cell walls, cytoplasmic membranes,
ribosomes, cytoplasm.
